Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-19 article.tex
edits to history
Add VQE diagram.

\section{History}
Molecules consist of various atoms and the elementary unit of an atom is electron and nucleus. When we consider atomic energy, electron-nuclei,
electron-electron interactions must be examined. Molecular energy consists of interactions between multiple atoms, including interactions between
 electrons from different atoms, as well as nuclei. Molecular energy can be pictured as a large package that contains many small balls, and the
 sum of the energy of their collisions is the sum of interactions between atoms.

@@

This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the
smallest eigenenergy.\\

>>>>

\section{History}
Molecules are composed of some collection of atoms, and the elementary units of the atom are the electron and the atomic nucleus. When we consider
 atomic energy, electron-nuclei, electron-electron interactions must be examined. Molecular energy consists of interactions between multiple atoms,
 including interactions between electrons from different atoms, as well as nuclei. Molecular energy can be pictured as a large package that contains
 many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.

@@

This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the smallest eigenenergy. The Figure \ref{VQE} illustrate the key outline of the VQE algorithm.
\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.75]{VQEdiagram.pdf}
\end{center}
\caption{VQE flowchart}\label{VQE}
\end{figure}
